Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-06-10 04_paper/Draft3.Rmd
Add files via upload

abstract: "China's international development finance has been long suspecpted to serve Beijing's efforts to promote its legitamcy and image on the world stage and to support closer ties with aid recipients. But what is puzzling is that these goals require transparency and publicity of development projects, which are two virtues China's development finance has historically lacked. We bring a novel perspective to this issue by considering how China's foreign aid complements more visible foreign policy levers Beijing may use to accomplish its goals: (1) state run media coverage of developing countries intended for foreign audiences and (2) bilateral diplomatic visits. These activities capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance is intended to support these goals, we expect greater coverage of a developing country in Chinese media directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation maps to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

@@

However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. @mattingly_when_2021 use experiments to demonstrate that investing in both foreign aid and public diplomacy efforts can improve China's image abroad and reduce concerns about the threat it poses. Importantly, both foreign aid and public diplomacy are scarce resources for building bilateral relationships and improving one's image abroad. It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and to invest in bilateral relationships through aid, mediated public diplomacy, and diplomatic visits.

We conceptualize two distinct but complementary modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionately larger China’s foreign aid. We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. Both dimensions are important to build its public diplomacy efforts. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.

@@

This work further helps in dispelling the notion that China purposely engages in development finance in secret. Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage. To our understanding, this is the first attempt to use media agenda-setting and public diplomacy to explain Chinese foreign aids allocations. At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to developing countries are all crucial to Beijing achieving its foreign policy goals and promoting its soft power.

@@

## First-level Agenda-setting

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public. That is, the public learns the importance of objects based on the amount of coverage that those objects receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972). More specifically, as @berelson_mass_1966 observe, “The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about” (p. 468). Since their seminal work, hundreds of studies have examined this media effect on the public. The vast majority support this agenda-setting notion (need some more extension or citations here).

@@

To extend this logic, media salience indicates significance for foreign countries named in the media. @wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S. The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.

## Selective Media Attention

With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention. From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air. News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.

@@

## Second-level Agenda-setting

@@

Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others (@entman_theorizing_2008; @kiousis_international_2008). Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes. Improving one's image to foreign audiences is the core objective of mediated public diplomacy.

As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency. It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy (@shambaugh_chinas_2015-1). It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires. The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea. It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format. Governments use media to tell its story to the world and improve its public relations with other countries. As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*. That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009).

@@

Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of *Xinhua* to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.

@@

Visiting leaders can increase the awareness of themselves and their country among citizens in the host country. @goldsmith_spinning_2009 find that the impact of high-level government visits on foreign publics' opinions is contextual. U.S. visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq. Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy. The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect. The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries (@goldsmith_does_2021). In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.

In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations. From the perspective of communication, diplomatic visit is a signal of support and proximity of the countries. The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.

@@

To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. The full dataset consists of unique recipient-year observations from 2000 to 2014.

@@

```{r, include=FALSE}
load(
  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
)
load(
  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/model_list1.R") 
)
reg.tab1 <- reg.tab
cat(reg.tab1)
```

@@

```{r, echo=FALSE}
coef_table <- map_dfr(
  model_list,
  ~ estimatr::tidy(lmtest::coeftest(.x))
) %>%
  filter(
    str_detect(term, "count") | 
      str_detect(term, "visits")
  ) %>%
  mutate(
    conf.low = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    term = rep(c("Coverage", "Visits"), len = n())
  ) %>%
  select(term, estimate, conf.low, conf.high)
tibble(
  "1" = coef_table$term[1:2],
  "2" = coef_table$estimate[1:2],
  "3" = " ",
  "4" = coef_table$estimate[3:4],
  "5" = " ",
  "6" = coef_table$estimate[5:6],
  "7" = " ",
  "8" = coef_table$estimate[7:8],
  "9" = " ",
  "10" = coef_table$estimate[9:10],
  "11" = " ",
  "12" = coef_table$estimate[11:12],
  "13" = " "
) %>% 
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  kable(booktabs = T,
        format = "latex",
        caption = "Table 1: Model Estimates",
        col.names = c(
          " ", rep(c("Est.", "95% CI"), len = 12)
        )) %>%
  kable_classic(full_width = F) %>%
  column_spec(
    3, image = spec_pointrange(
      x = coef_table$estimate[1:2],
      xmin = coef_table$conf.low[1:2],
      xmax = coef_table$conf.high[1:2],
      vline = 0
    )
  ) %>%
  column_spec(
    5, image = spec_pointrange(
      x = coef_table$estimate[3:4],
      xmin = coef_table$conf.low[3:4],
      xmax = coef_table$conf.high[3:4],
      vline = 0
    )
  ) %>%
  column_spec(
    7, image = spec_pointrange(
      x = coef_table$estimate[5:6],
      xmin = coef_table$conf.low[5:6],
      xmax = coef_table$conf.high[5:6],
      vline = 0,
      lim = c(0, max(coef_table$conf.high[5:6]))
    )
  ) %>%
  column_spec(
    9, image = spec_pointrange(
      x = coef_table$estimate[7:8],
      xmin = coef_table$conf.low[7:8],
      xmax = coef_table$conf.high[7:8],
      vline = 0
    )
  )%>%
  column_spec(
    11, image = spec_pointrange(
      x = coef_table$estimate[9:10],
      xmin = coef_table$conf.low[9:10],
      xmax = coef_table$conf.high[9:10],
      vline = 0
    )
  ) %>%
  column_spec(
    13, image = spec_pointrange(
      x = coef_table$estimate[11:12],
      xmin = coef_table$conf.low[11:12],
      xmax = coef_table$conf.high[11:12],
      vline = 0
    )
  ) %>%
  add_header_above(
    c(
      " " = 1,
      "Linear" = 2,
      "Tobit" = 2,
      "Selection" = 2,
      "Level" = 2,
      "IV Lag" = 2,
      "IV Lewbel" = 2
    )
  ) %>% cat

```

@@

>>>>

abstract: "Absent formal avenues of transparency, how do China's efforts at gaining international recognition and promoting good relations with aid recipients play out in Beijings foreign aid giving? We bring a novel perspective to this issue by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. To test this expectation we merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China’s broader diplomacy and legitimacy seeking objectives on the world stage."
---

@@

However, many observe an unmistakable connection between China’s version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls “South-South cooperation.” While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. @mattingly_when_2021 use experiments to demonstrate that investing in both foreign aids and public diplomacy efforts can improve its image abroad and reduce concerns about the threat it poses. Both foreign aids and public diplomacy are scarce resources for government to build bilateral relationships and improve its image abroad. It is plausible to expect governments find a cluster of foreign countries to be strategically important partners, and invest in bilateral relationships through aids, mediated public diplomacy and diplomatic visits. To our knowledge, none of the existing studies systematically examine which countries are “friends” to get more benefits of aids from the perspective of Beijing’s diplomacy efforts. We conceptualize two opposite modes of interactions from the face value between foreign aids and media/public diplomacy: secret and open. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We argue that countries that receive higher media exposure and diplomacy efforts are strategically more important to Beijing, and in turn receive disproportionally larger China’s foreign aid. We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China’s bilateral diplomatic activities. Both dimensions are important to building its public diplomacy efforts. These measures capture two distinct but related aspects of China’s foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China’s development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving. All else equal, we argue that developing countries that receive higher media coverage and diplomatic visit are strategically more important than the others.

@@

This work further helps in dispelling the notion that China purposely engages in development finance in secret. Much to the contrary, China complements its aid giving with visible diplomatic envoys and greater external-facing media coverage. To our understanding, this is the first attempt to use media agenda-setting and public diplomacy decision to explain Chinese foreign aidS allocations. At the end of the day, government-sponsored communication, diplomatic outreach, and financial assistance to aid-needed developing countries, are all crucial to achieving a state’s foreign policy goals and promoting its soft power.

@@

## First-level Agenda-setting and Selective Media Attention

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public. That is, the public learns the importance of objects based on the amount of coverage that those objects receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972). More specifically, as @berelson_mass_1966 observe, “The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about” (p. 468). Since their seminal work, hundreds of studies have examined the agenda-setting effect on the public. The vast majority support this agenda-setting notion (need some more extension or citations here).

@@

To extend this logic, media salience indicates significance for foreign countries named in the media. @wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S.. The countries' media coverage will lead to the countries becoming more salient among the public.

With the implication of the media salience in mind, news editor is a source of gatekeeping power for those who can tell us where to focus our attention. From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air. News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.

@@

## Xinhua’s Effforts to Set Agenda

@@

Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others (@entman_theorizing_2008; @kiousis_international_2008). Compared to the first-level agenda-setting, this mechanism entails a more profound media influence on shaping public attitudes in the public’s perceptions. Since news media have a significant impact on shaping the public's perceptions, investing in international news markets to improve one's image to foreign audiences is the core objective of mediated public diplomacy.

As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency. It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy (@shambaugh_chinas_2015-1). It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires. The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea. It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format. Governments use media to tell their story to the world and improve their public relations with other countries. As such, scholars often focus on China's mediated public diplomacy efforts through *Xinhua*. That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009).

@@

Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit the information as a credible news outlet. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of *Xinhua* to report global affairs, editors’ choices reflect which countries are more than the others to receive media coverage.

@@

Visiting leaders can increase the awareness of themselves and their country among citizens in the host country. @goldsmith_spinning_2009 find that the impact of high-level government visits on foreign publics' opinions is contextual. U.S. visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq. Again, the credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy. The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect. The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries (@goldsmith_does_2021). In most cases, the host leader has the leverage to provide news frames for the journalists to report the government-to-government visit positively.

In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations. From the perspective of communication, diplomatic visits signal the countries' support and proximity. The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.

@@

To assess complementarities between China's bilateral diplomatic visits and **Xinhua** coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData’s Chinese development finance dataset with two newly available datasets: (1) AidData’s compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition **Xinhua** news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. The full dataset consists of unique recipient-year observations from 2000 to 2014.

@@

```{r, include=FALSE}
load(
  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
)
reg.tab1 <- reg.tab
cat(reg.tab1)
```

@@

@@

# References
In the above, subscript $r$ indexes the aid recipient and $t$ the year. The vector $X_{rt}$ is the set of recipient and bilateral controls, and $\epsilon_{rt}$ is a zero-centered stochastic term.

In the event that the process that determines whether countries receive aid from China differs from the process that determines the amount of aid given, we further separate the estimation into selection and level equations as outlined by Cragg (year?). The selection equation is estimated using mixed effects logit with random recipient intercepts and the level equation is estimated using OLS with cluster-robust standard errors.

Finally, because within-year coverage and visits may have greatest relevance for predicting the response, using the lag of each variable in model estimation may under-estimate the complementarities between coverage and visits with aid. However, estimating the models using same-year coverage and visits poses a challenge due to likely endogeneity between them and the response. Unable to find a satisfactory set of instruments

```{r, results='asis', eval=F}
load(
  paste0(stringr::str_remove(getwd(), "/04_paper"), "/03_analysis/tab1.R")
)
reg.tab1 <- reg.tab
cat(reg.tab1)
```
